Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-03-30 manuscript.Rmd
Changed pupiltargets to pupilmasks

    temp <- c(pupilmasks[,,startindex+level],pupiltargets[,,startindex+level+5])
        cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
    cleanmasksP[cond,level] <- mean(temp[i])}

>>>>

    temp <- c(pupilmasks[,,startindex+level],pupilmasks[,,startindex+level+5])
        cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
    cleanmasksP[cond,level] <- mean(temp[i])}
